Quantum Pseudo-Telepathy

### 2023-06-29 paper/main.tex
column circuits

{\renewcommand{\arraystretch}{2}
\begin{figure}
  \centering
  \[\begin{array}{|*{2}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}|}
      \hhline{---}
      (I \otimes I) (Z \otimes I) (I \otimes I) & (I \otimes I) (I \otimes Z) (I \otimes I) & \cnot (I \otimes Z) \cnot
      \\ \hhline{---}
      (H \otimes I) (Z \otimes I) (H \otimes I) & (I \otimes H) (I \otimes Z) (I \otimes H) & (H \otimes H) (Z \otimes Z) (H \otimes H)
      \\ \hhline{---}
      (H \otimes Y) (Z \otimes Z) (H \otimes Y) & (Y \otimes H) (Z \otimes Z) (Y \otimes H) &
       (S \otimes S) (X \otimes X) (S^{*} \otimes S^{*}) 
      \\ \hhline{---}
    \end{array}\]
  \caption{Unitary transformations required for measuring in the
    different basis. The actual basis measured is the middle
    term of each cell, which, after expanding, is either
    \(Z \otimes I\) or \(I \otimes Z\). For example, in the last
    cell, \(X \otimes X\) evaluates to
    \((H \otimes H) (Z \otimes Z) (H \otimes H)\).
    \(Z \otimes Z\), in turn, becomes \(\cnot (I \otimes Z) \cnot\), meaning that
    we measure the second qubit in the computational basis.\label{fig:change-basis}}
\end{figure}}

@@

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}[column sep=0.25cm]
      \lstick{\(A_{0}\)}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{Y}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{S}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{S^*}
      \\
      \lstick{\(A_{1}\)}
      & \gate{Y}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{0}}
      & \targ{}
      & \gate{Y}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{1}}
      & \targ{}
      & \gate{S}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{2}}
      & \targ{}
      & \gate{H}
      & \gate{S^*}
    \end{quantikz}
    \caption{Quantum circuit for measuring the third row.\label{fig:circ-row2}}
  \end{figure}
\end{description}

>>>>

{\renewcommand{\arraystretch}{2}
  \begin{figure}
    \centering
    \[\begin{array}{|*{2}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}|}
        \hhline{---}
        (I \otimes I) (I \otimes Z) (I \otimes I) & (I \otimes I) (Z \otimes I) (I \otimes I) & \cnot (I \otimes Z) \cnot
        \\ \hhline{---}
        (H \otimes I) (Z \otimes I) (H \otimes I) & (I \otimes H) (I \otimes Z) (I \otimes H) & (H \otimes H) (Z \otimes Z) (H \otimes H)
        \\ \hhline{---}
        (H \otimes Y) (Z \otimes Z) (H \otimes Y) & (Y \otimes H) (Z \otimes Z) (Y \otimes H) &
                                                                                                (S \otimes S) (X \otimes X) (S^{*} \otimes S^{*}) 
        \\ \hhline{---}
      \end{array}\]
    \caption{Unitary transformations required for measuring in the
      different basis. The actual basis measured is the middle
      term of each cell, which, after expanding, is either
      \(Z \otimes I\) or \(I \otimes Z\). For example, in the last
      cell, \(X \otimes X\) evaluates to
      \((H \otimes H) (Z \otimes Z) (H \otimes H)\).
      \(Z \otimes Z\), in turn, becomes \(\cnot (I \otimes Z) \cnot\), meaning that
      we measure the second qubit in the computational basis.\label{fig:change-basis}}
  \end{figure}}

@@

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}[column sep=0.25cm]
      \lstick{\(A_{0}\)}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{Y}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{S}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{S^*}
      \\
      \lstick{\(A_{1}\)}
      & \gate{Y}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{0}}
      & \targ{}
      & \gate{Y}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{1}}
      & \targ{}
      & \gate{S}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{2}}
      & \targ{}
      & \gate{H}
      & \gate{S^*}
    \end{quantikz}
    \caption{Quantum circuit for measuring the third row.\label{fig:circ-row2}}
  \end{figure}

\item[Column 0:] When assigned the first column, Bob performs the measurements
  \(I \otimes Z, X \otimes I\) and \(-X \otimes Z\), which the circuit
  in Figure~\ref{fig:circ-col0} implements.

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}
      \lstick{\(B_{0}\)}
      & \gate{H}
      & \metercw[label style={inner sep=1pt}]{b_{1}}
      &
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      &
      \\
      \lstick{\(B_{1}\)}
      &
      & \metercw[label style={inner sep=1pt}]{b_{0}}
      & \gate{Y}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{b_{1}}
      & \targ{}
      & \gate{Y}
      &
    \end{quantikz}
    \caption{Quantum circuit for measuring the first column.\label{fig:circ-col0}}
  \end{figure}

\item[Column 1:] When assigned the second column, Bob performs the measurements
  \(Z \otimes I, I \otimes X\) and \(-Z \otimes X\), which the circuit
  in Figure~\ref{fig:circ-col1} implements.

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}
      \lstick{\(B_{0}\)}
      & 
      & \metercw[label style={inner sep=1pt}]{b_{0}}
      & \gate{Y}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{Y}
      &
      \\
      \lstick{\(B_{1}\)}
      & \gate{H}
      & \metercw[label style={inner sep=1pt}]{b_{1}}
      & 
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{b_{2}}
      & \targ{}
      & \gate{H}
      &
    \end{quantikz}
    \caption{Quantum circuit for measuring the second column.\label{fig:circ-col1}}
  \end{figure}

\item[Column 2:] When assigned the third column, Bob performs the measurements
  \(Z \otimes Z, X \otimes X\) and \(Y \otimes X\), which the circuit
  in Figure~\ref{fig:circ-col2} implements.

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}[column sep=0.25cm]
      \lstick{\(B_{0}\)}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{S}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{S^*}
      &
      \\
      \lstick{\(B_{1}\)}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{b_{0}}
      & \targ{}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{b_{1}}
      & \targ{}
      & \gate{H}
      & \gate{S}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{b_{2}}
      & \targ{}
      & \gate{H}
      & \gate{S^*}
      &
    \end{quantikz}
    \caption{Quantum circuit for measuring the third column.\label{fig:circ-col2}}
  \end{figure}
\end{description}
